---
title: "Developing Data Products Week 3: R Markdown and Plotly"
author: "xbuRAw (GH)"
date: "December 29, 2019"
geometry: margin=2cm
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = TRUE, warning = FALSE, message = FALSE)
```

## 0. Introduction
In this small project we will try out different plots that the `plotly` library has to offer.
We will utilize `plotly` to produce:

1. a simple line plot 
2. a histogram
3. a boxplot
4. a multidimensional plot in 2D

```{r}
library(plotly)
```
data sets being used:

```{r}
data(presidents)
data(sunspot.year)
data(mtcars)
```

## 1.1 Line plot 
A simple line plot of the quarterly approval ratings of US presidents.

```{r eval = FALSE}
plot_ly(data = as.data.frame(presidents), x = ~time(presidents),
  y = ~presidents, type = "scatter", mode = "lines") %>%
  layout(title = "Quarterly approval ratings over the years")
```
##
```{r echo = FALSE}
plot_ly(data = as.data.frame(presidents), x = ~time(presidents), y = ~presidents, type = "scatter", mode = "lines") %>%
  layout(title = "Quarterly approval ratings over the years")
```

## 1.2 Histogram
A histogram of monthly sunspots numbers (1749-1983).

```{r eval = FALSE}
p <- plot_ly(data = as.data.frame(sunspot.year), x = ~sunspot.year,
  type = "histogram") %>%
  layout(title = "Sunspot occurrences histogram",
    yaxis = list(title = "count"))
p
```
##
```{r echo = FALSE}
p <- plot_ly(data = as.data.frame(sunspot.year), x = ~sunspot.year, type = "histogram") %>%
  layout(title = "Sunspot occurrences histogram", yaxis = list(title = "count"))
p
```

## 1.3 Box plot
A boxplot visualizing the horsepower by cylinder relationship in the mtcars data set.

```{r eval = FALSE}
plot_ly(mtcars, x=~cyl, y = ~hp,
  color = ~as.factor(cyl), type = "box") %>%
  layout(title = "Box plot cyl~hp")
```
##
```{r echo = FALSE}
plot_ly(mtcars, x=~cyl, y = ~hp, color = ~as.factor(cyl), type = "box") %>%
  layout(title = "Box plot cyl~hp")
```

## 1.4 Multi dimensional plot
A 2D plot visualizing 4 dimensions of the mtcars data set (x-axis (weight), y-axis (miles per galon), color (cylinder) and size (horse power) of data point).

```{r eval = FALSE}
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
  color = ~as.factor(cyl), size = ~hp,
  type = "scatter", mode = "markers") %>%
  layout(title = "Car properties visualized")
```
##
```{r echo = FALSE}
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
  color = ~as.factor(cyl), size = ~hp,
  type = "scatter", mode = "markers") %>%
  layout(title = "Car properties visualized")
```